Assessing Ranking Fidelity of Competition Structures via Weighted Mutual Information

### 2025-10-10 CMSAC_presentation.Rmd
new intro slides draft

@@

<!-- Should these plots be on separate slides? -->
```{r out.width="49%", fig.show='hold', fig.align='center'}
knitr::include_graphics("tournament_comparison_plot.png")
knitr::include_graphics("tournament_comparison_plot_close.png")
```

>>>>

## New Slide - Extreme Tournament

- 4 team single elimination tournament:
  - Dream Team vs Work Group vs Middle School Girls Team vs Babies
- If we only care about the top team winning, seeding structure does not matter
- If we care about who gets second and third, seeding becomes important
  - Would not pair up Work Group and Dream Team in the first round

## New

- Comparing different competition structures, which competition structure is best?

- Efficacy: Final rankings should match the true rankings of the strength of the competitors

- Effectivity: Interested in correctly ranking the best competitor as first

CITEE

## New

- Other competitions where the correct ranking of some, but not all, of the competitors is of import
  - Olympic competition ranks the top 3 competitors

- "Salient ranks": the ranks of a competition structure that matter
  - Efficacy: 1 through $n$ matter
  - Effectivity: 1 is only salient rank

- We will propose a metric that quantifies how effectively different tournament structures convey information about competitors’ true strengths

@@

<!-- Should these plots be on separate slides? -->
```{r out.width="49%", fig.show='hold', fig.align='center'}
knitr::include_graphics("tournament_comparison_plot.png")
#knitr::include_graphics("tournament_comparison_plot_close.png")
```
